Labeled object representation and manipulation with ITK

### 2007-05-15 article/Article.tex
StatisticsLabelCollectionImageFilter is now multithreaded
darcs-hash:20070515095232-2fc9d-13fc7dfe7cd72dd8ca62f4badc3d82348c7c31b8.gz

@@

Also, more attributes will be implemented, like the perimeter estimation, the usual moments, etc.

>>>>

The classes {\em itk::ShapeLabelObject} and {\em itk::StatisticsLabelObject} have been
created to reduce the number of filters made to manipulate the attributes, and to make
the computation of all the set of attributes much efficient. In the early stage of
development, all the attributes were managed as in {\em AttributeLabelObject}, and
a set of 8 classes made to manipulate a single were provided, leading to a huge
number of classes.

@@

Also, more attributes will be implemented, like the perimeter estimation, the usual moments, etc. It may be useful to implement the most commonly used opening, keep N objects and relabel transforms in a more efficient way, by using an {\em AttributeLabelObject} instead of a {\em ShapeLabelObject} or a {\em StatisticsLabelObject}.

All the {\em Shape} filters are currently able to use the Feret diameter only in 2D images. For the other dimensions, the feret diameter is not computed, and so always get a value of $0$. The computation of the Feret diameter should be forced if the user want to use it.
